### 2009-04-03 talk/icooolps2009-dotnet/paper.tex
Typos.

\begin{abstract}
The CLI, i.e. the virtual machine at the core of the .NET environment, is a
statically typed virtual machine.  Although it is being used as a target for
many different languages, it is hard to provide higly efficient implementation
of languages whose model is too different than the one of the VM.  In
particular, dynamically typed languages are typically order of magnitude
slower than, e.g., C\#.

@@

JIT compilation for .NET means to generate .NET bytecode at runtime, which
will further compiled down to machine code by .NET's own JIT compiler.  The
main and novel contribution of this paper is to show that this
\emph{two-layers JIT} technique is effective, and can give very high speedups,
up to make dynamic languages faster than C\# itself under certain
circumstances.

>>>>

\begin{abstract}
The CLI, i.e. the virtual machine at the core of the .NET environment, is a
statically typed virtual machine.  Although it is being used as a target for
many different languages, it is hard to provide highly efficient implementation
of languages whose model is too different than the one of the VM.  In
particular, dynamically typed languages are typically order of magnitude
slower than, e.g., C\#.

@@

JIT compilation for .NET means to generate .NET bytecode at runtime, which
will be further compiled down to machine code by .NET's own JIT compiler.  The
main and novel contribution of this paper is to show that this
\emph{two-layers JIT} technique is effective, and can give very high speedups,
up to making dynamic languages faster than C\# itself under certain
circumstances.
